Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-28 main_revision.tex

The Caxiuan\~a site (CAX) experienced substantial drought stress and little nutrient stress ($B_{tran,mn}$ $\sim$0.6, PNU$\sim$13\%). Niwot Ridge (NWR) experienced substantial amounts of drought and N limitation, ($B_{tran,mn}$, $\sim$0.55, PNU$\sim$21\%). Harvard Forest (HVF) site had very little drought stress, and moderate N limitation ($B_{tran,mn}$ $\sim$0.96, PNU$\sim$15\%).  Metolius (MET)  had some drought stress and the least nutrient stress ($B_{tran,mn}$ $\sim$0.86, PNU$\sim$10\%).  
Thus, the sites chosen span a range of initial limiting conditions.  
Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

\subsubsection{Parametric control over system state}
At all sites, specific leaf area (\emph{slatop}) has a large first-order impact on LAI, and on leaf N concentrations (Figure \ref{NR1 state}), as expected, since it is used directly in the calculation of both of these quantities. For GPP, the impact of SLA is always positive, despite the higher LAI causing lower N per unit area of leaf (which reduces per-unit leaf area photosynthetic capacity). The impact of SLA on NPP can, however, be negative (CAX, NWR), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance at high LAI. At Niwot Ridge, the parameter range straddles an optimal SLA (or local maximum at the second-largest parameter values) for NPP, again reflecting the assimilation/respiration cost trade-off.

Root:leaf ratio (\emph{froot\_leaf}) has 1) a direct effect on LAI, via changes in allocation fractions to different tissues, 2) an indirect effect on NPP, given the modified maintenance costs of the resultant fine root biomass pools, 3) an effect on the uptake of water via root biomass and 4) an effect on nutrient limitation through root-mediated N uptake costs.  The first two impacts decrease NPP with \emph{froot\_leaf} and the latter two increase it.  Both types of effect are seen here, with the Niwot Ridge and Metolius sites (which have the lowest productivity and LAI, and thus presumably very low root biomass in the first place) suffering very large reductions in GPP, NPP, and LAI at low \emph{froot\_leaf} ratios, reflecting mechanisms 3 and 4.  Harvard forest and Caxiuan\~a both show increases in all variables with low \emph{froot\_leaf}.  In Figure \ref{btran state}, we can see that low \emph{froot\_leaf} is a primary control over drought stress at Metolius, in particular.

>>>>

The Caxiuan\~a site (CAX) experienced substantial drought stress and little nutrient stress ($B_{tran,mn}$ $\sim$0.6, PNU$\sim$13\%). Niwot Ridge (NWR) experienced substantial amounts of drought and N limitation, ($B_{tran,mn}$, $\sim$0.55, PNU$\sim$21\%). Harvard Forest (HVF) site had very little drought stress, and moderate N limitation ($B_{tran,mn}$ $\sim$0.96, PNU$\sim$15\%).  Metolius (MET)  had some drought stress and the least nutrient stress ($B_{tran,mn}$ $\sim$0.86, PNU$\sim$10\%).

Thus, the sites chosen span a range of initial limiting conditions.  
Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

\subsubsection{Parametric control over system state}
At all sites, specific leaf area (\emph{slatop}) has a large first-order impact on LAI, and on leaf N concentrations (Figure \ref{NR1 state}), as expected, since it is used directly in the calculation of both of these quantities. The impact of SLA on GPP is always positive, despite the thinner leaves having lower N, and thus lower photosynthetic capacity, per unit area of leaf. The impact of SLA on NPP can, however, sometimes be negative (CAX, NWR), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance at high LAI.

Root:leaf ratio (\emph{froot\_leaf}) has 1) a direct effect on LAI, via changes in tissue allocation fractions , 2) an indirect effect on NPP, via changes in maintenance costs of fine root pools, 3) an effect on the uptake of water via root biomass and 4) an effect on nutrient limitation through root-mediated N uptake costs.  The first two impacts decrease NPP with higher \emph{froot\_leaf} costs and the latter two increase it via \emph{froot\_leaf} benefits. CAX and NWR exhibit higher LAI with fewer roots, HVF exhibits lower LAI with fewer roots, and MET

Both types of effect are seen here, with the Niwot Ridge and Metolius sites (which have the lowest productivity and LAI, and thus presumably very low root biomass in the first place) suffering very large reductions in GPP, NPP, and LAI at low \emph{froot\_leaf} ratios, reflecting mechanisms 3 and 4.  Harvard forest and Caxiuan\~a both show increases in all variables with low \emph{froot\_leaf}.  In Figure \ref{btran state}, we can see that low \emph{froot\_leaf} is a primary control over drought stress at Metolius, in particular.
